raptr: Representative and Adequate Prioritization Toolkit in R

### 2017-03-18 code/rmarkdown/article.Rmd
fix bug in benchmark fix Jonathon's affiliation in ms

---
title: "raptr: Representative and Adequate Prioritization Toolkit in R"
author: |
  | Jeffrey O. Hanson$^1$, Jonathan R. Rhodes$^2$, Hugh P. Possingham$^{1,3}$, Richard A. Fuller$^1$
  | $^1$School of Biological Sciences, The University of Queensland, Brisbane, QLD, Australia
  | $^2$School of Geography, Planning and Environmental Management, The University of Queensland, Brisbane, QLD, Australia
  | $^3$The Nature Conservancy, South Brisbane, QLD, Australia
  | Correspondance should be addressed to jeffrey.hanson@uqconnect.edu.au
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  rmarkdown::pdf_document:
    toc: false
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: preamble.tex
fontsize: 11pt
documentclass: article
subparagraph: true
bibliography: references.bib
csl: reference-style.csl
---

@@

1. An underlying aim in conservation planning is to maximize the long-term persistence of biodiversity. To fulfill this aim, the ecological and evolutionary processes that sustain biodiversity must be preserved. One way to conserve such processes at the feature level (eg. species, ecosystem) is to preserve a sample of the feature (eg. individuals, areas) that is representative in terms of the intrinsic or extrinsic physical attributes that underpin the process of interest. For example, by conserving a sample of populations with local adaptations that is representative in terms of the full variation found in the species--physical attributes associated with adaptation--protected areas can foster adaptative processes by ensuring these adaptations are not lost. Despite this, current reserve selection methods overwhelmingly focus on securing an adequate amount of area or habitat for each feature. Little attention has been directed towards capturing a representative sample of each feature.

>>>>

---
title: "raptr: Representative and Adequate Prioritization Toolkit in R"
author: |
  | Jeffrey O. Hanson$^1$, Jonathan R. Rhodes$^2$, Hugh P. Possingham$^{1,3}$, Richard A. Fuller$^1$
  | $^1$School of Biological Sciences, The University of Queensland, Brisbane, QLD, Australia
  | $^2$School of Earth and Environmental Sciences, The University of Queensland, Brisbane, QLD, Australia
  | $^3$The Nature Conservancy, South Brisbane, QLD, Australia
  | Correspondence should be addressed to jeffrey.hanson@uqconnect.edu.au
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  rmarkdown::pdf_document:
    toc: false
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: preamble.tex
fontsize: 11pt
documentclass: article
subparagraph: true
bibliography: references.bib
csl: reference-style.csl
---

@@

1. An underlying aim in conservation planning is to maximize the long-term persistence of biodiversity. To fulfill this aim, the ecological and evolutionary processes that sustain biodiversity must be preserved. One way to conserve such processes at the feature level (eg. species, ecosystem) is to preserve a sample of the feature (eg. individuals, areas) that is representative in terms of the intrinsic or extrinsic physical attributes that underpin the process of interest. For example, by conserving a sample of populations with local adaptations that is representative in terms of the full variation found in the species--physical attributes associated with adaptation--protected areas can foster adaptive processes by ensuring these adaptations are not lost. Despite this, current reserve selection methods overwhelmingly focus on securing an adequate amount of area or habitat for each feature. Little attention has been directed towards capturing a representative sample of each feature.
